Real-Time Estimation of COVID-19 Infections: Deconvolution and Sensor Fusion

### 2022-02-27 paper/paper.tex
fix minor typo

As for the two extensions presented in \eqref{eq:tf_realtime4}, the natural  
trend filtering constraints can be be enfored by introducing a linear
interpolant matrix as described in Section~11.2 of \citet{tibshirani2020divided}.
This effectively replaces the convolution matrix \smash{$\hP$} and the 3$\rd$
difference operator $D$, in the ADMM steps above, by \smash{$\tP$} and
\smash{$\tD$}, respectively, which are given by right multiplying $P$ and $D$ by
the interpolant matrix.

>>>>

As for the two extensions presented in \eqref{eq:tf_realtime4}, the natural  
trend filtering constraints can be be enforced by introducing a linear
interpolant matrix as described in Section~11.2 of \citet{tibshirani2020divided}.
This effectively replaces the convolution matrix \smash{$\hP$} and the 3$\rd$
difference operator $D$, in the ADMM steps above, by \smash{$\tP$} and
\smash{$\tD$}, respectively, which are given by right multiplying $P$ and $D$ by
the interpolant matrix.
